Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-10-27 man/figures/ring_climate.Rmd
add new figure

##### 
**Figure 6.** Correlation coefficients obtained by relating tree-ring residual chronologies (RWI) of *Q. pyrenaica* and monthly climatic data: precipitation (a), 6-month SPEI (b), maximun (c) and minimun (d) temperatures. *green* bars: northern site (SJ); *light blue* bars: low-elevation southern site (CA-Low); and *dark blue* bars: high-elevation shouthern site (CA-High). Asteriks indicate significant ($P < 0.05$) correlation coefficients.

```{r}
rtmax <- read.csv(here("data/rwi_climate", "rtmax_selected.csv"), header = TRUE, sep = ',')
rtmin <- read.csv(here("data/rwi_climate", "rtmin_selected.csv"), header = TRUE, sep = ',')
rsequia <- read.csv(here("data/rwi_climate", "rsequia_selected.csv"), header = TRUE, sep = ',')
rprec <- read.csv(here("data/rwi_climate", "rprec_selected.csv"), header = TRUE, sep = ',')

rtmax <- rtmax %>% mutate(v_name = 'T max')
rtmin <- rtmin %>% mutate(v_name = 'T min')
rsequia <- rsequia %>% mutate(v_name ='SPEI')
rprec <- rprec %>% mutate(v_name = 'Prec')

@@

p_tmax <- df %>% filter(v_name == 'T max') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'bottom') + 
  ylab('') + 
  annotate("text", x = 2, y = 0.35, label = "T max", fontface =2, size = 5)

p_tmin <- df %>% filter(v_name == 'T min') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.6), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'top') + 
  ylab('') +
  annotate("text", x = 2, y = 0.35, label = "T min", fontface =2, size = 5)

@@

p_prec_spei <- dfprec_spei %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  geom_vline(xintercept=20) +
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.2, 0.8), 
                     breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8)) +
  scale_x_continuous(breaks = labelitas$id, labels = labelitas$month_name, position = 'top') + 
  ylab('') +
  annotate("text", x = 2, y = 0.75, label = "Prec", fontface =2, size = 5) + 
  annotate("text", x = 23, y = 0.75, label = "SPEI", fontface =2, size = 5)

ptmin

@@

p_prec_spei + theme(legend.position="none") + ptemperatura + plot_layout(ncol=1, heights = c(2,3), tag_level = 'keep')  + plot_annotation(tag_levels = c('a','b'))

```

>>>>

##### 
**Figure 6.** Correlation coefficients obtained by relating tree-ring residual chronologies (RWI) of *Q. pyrenaica* and monthly climatic data: precipitation and 6-month SPEI (a), minimun (b) and maximun (c) temperatures. *green* bars: northern site (SJ); *light blue* bars: low-elevation southern site (CA-Low); and *dark blue* bars: high-elevation shouthern site (CA-High). Asteriks indicate significant ($P < 0.05$) correlation coefficients.

```{r}
rtmax <- read.csv(here("data/rwi_climate", "rtmax_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name = 'T max')
rtmin <- read.csv(here("data/rwi_climate", "rtmin_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name = 'T min')
rsequia <- read.csv(here("data/rwi_climate", "rsequia_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name ='SPEI')
rprec <- read.csv(here("data/rwi_climate", "rprec_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name = 'Prec')

@@

p_tmax <- df %>% filter(v_name == 'T max') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'bottom') + 
  ylab('Correlation') + 
  annotate("text", x = 2, y = 0.35, label = "T max", fontface =2, size = 5)

p_tmin <- df %>% filter(v_name == 'T min') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.6), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.35, label = "T min", fontface =2, size = 5)

@@

p_prec_spei <- dfprec_spei %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  geom_vline(xintercept=20) +
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.2, 0.8), 
                     breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8)) +
  scale_x_continuous(breaks = labelitas$id, labels = labelitas$month_name, position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.75, label = "Prec", fontface =2, size = 5) + 
  annotate("text", x = 23, y = 0.75, label = "SPEI", fontface =2, size = 5)

@@

ring_climate <- p_prec_spei + theme(legend.position="none") + ptemperatura + plot_layout(ncol=1, heights = c(2,3), tag_level = 'keep')  + plot_annotation(tag_levels = c('a','b'))

ring_climate
```
